A Possibilistic Valid-time Model

### 2011-12-13 ipmu2012/conclusions.tex
Also the conclusions...

We presented a valid-time model to represent and querying ill-known temporal intervals. The main advantage of the framework is that it is always possible to get both a possibility and a necessity measures for every comparison, which is also useful for ranking purposes. The framework models the Allen's relations and it has the flexibility to model specific and more complex relations by means of ill-known constraints.  As future work, the time interval in the query specification would also be ill-known.

>>>>

We presented a Valid-time model to represent and query ill-known temporal intervals. The main advantage of this framework is that it works with ill-known intervals and thus tries to correctly represents and handle querying temporal uncertainty in the database. The final ranking step provides a usefull result record set. The framework models the Allen relations and it has the flexibility to model specific and more complex relations by means of ill-known constraints. As future work, allowing the time interval in the query specification to be ill-known is considered.
